### 2025-04-17 Manuscript/Manuscript.tex
writting

\subsection{Gram matrix formulation}
Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n}\\
		\vdots & \vdots & \ddots & \vdots\\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
	\end{pmatrix},
\end{equation*}
i.e., $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, we have,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n}\\
		\vdots & \vdots & \ddots & \vdots\\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
	\end{pmatrix}.
\end{equation*}

Notice this matrix is Hermitian by construction,
\begin{align*}
\mathcal{G}_{i,j}^* = (\braket{\psi_i|\psi_j})^* = \braket{\psi_j|\psi_i} = \mathcal{G}_{j,i}.
\end{align*}

The Gram matrix allows us to reframe the exclusion problem in a more abstract and basis-independent form. Since $\mathcal{G}$ is hermitian and positive semi-definite, we can write,
\begin{align*}
\mathcal{G} = X^\dagger X,
\end{align*}
for some matrix $X$ whose columns are the pure states,
\begin{align*}
	X = \begin{pmatrix}
		\mid & \mid &        & \mid \\
		\ket{\psi_1} & \ket{\psi_2} & \dots & \ket{\psi_n} \\
		\mid & \mid &        & \mid
	\end{pmatrix}.
\end{align*}
Notice the diagonal elements of $X$ are,
\begin{align*}
	X_{i,i}=\braket{\omega_i|\psi_i}
\end{align*}
For an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$. \footnote{It is important to remark that fixing the basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$ fixes the decomposition of $G=X^\dagger X$ and vice versa.}

Let us consider an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$, and define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$. Then, the \gls{sdp} formulation for the ensemble $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ can be expressed as the following,
\begin{align*}
	\tr(\Pi_i \rho_i) &= \tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
	&= |\braket{\omega_i|\psi_i}|^2 \\
	&= |X_{i,i}|^2.
\end{align*}

Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as,
\begin{align*}
	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i},\\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

Similarly, the success probability becomes, 
\begin{align*}
	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i}\right),\\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

This reformulation highlights that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems, in both \gls{me} and \gls{ze} protocols, are equivalent. That is, the optimal success and error probabilities are identical in both systems. Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.

Moreover, we remark we are not especially interested in the arbitrary prior probabilities $\eta_i$ scenario, since the result for equal prior probabilities $\eta_i=\frac{1}{n}$ can be easily extended to the previous case, with $n$ as the number of states. This extension can be performed by considering the non-normalized states
\begin{align*}
	\ket{\tilde{\psi_i}}=\frac{1}{\sqrt{\eta_i}}\ket{\psi_i}
\end{align*}
and reformulate the problem in terms of this new states forgetting about the prior probabilities since they are encoded inside the states. Thus, for simplicity we will consider the equal probabilities case.

@@

Given a quantum state $\ket{\psi}$, which we refer to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$. Specifically, if the ensemble consists of a total of $n$ quantum states, then its elements are of the form,
\begin{align*}
	U_i\ket{\psi}, \quad i \in \{1, \dots, n\},
\end{align*}
where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix product. In terms of density matrices, the ensemble can equivalently be written as:
\begin{align*}
	\rho_i = U_i \rho U_i^\dagger, \quad i \in \{1, \dots, n\},
\end{align*}
where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix corresponding to the seed state.

For instance, let $\mathcal{U}$ be a unitary operator such that $\mathcal{U}^n = \mathds{1}$ (i.e., $\mathcal{U}$ generates a cyclic group of order $n$). Then, the set of states
\begin{align*}
	\left\{ \mathcal{U}^i\ket{\psi} \right\}_{i=0}^{n-1}
\end{align*}
forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$. This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent section.

\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state. The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are nothing but,
\begin{align*}
	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \braket{\psi | \mathcal{U}^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
\end{align*}
where we use the shorthand notation
\begin{align*}
	\braket{\mathcal{U}^k}_\psi := \braket{\psi | \mathcal{U}^k | \psi}.
\end{align*}

@@

Note the Gram matrix is Hermitian, as required, since,
\begin{align*}
    \braket{\mathcal{U}^{-j}}_{\psi} = \braket{\psi | U^{-j} | \psi} = \left(\braket{\psi | U^j | \psi}\right)^* = \braket{\mathcal{U}^j}_{\psi}^*.
\end{align*}
Additionally, by using the identity $\mathcal{U}^n = \mathds{1}$, we can simplify terms such as,
\begin{align*}
	\braket{\mathcal{U}^{-n+i}}_\psi = \braket{\psi | \mathcal{U}^{-n+i} | \psi} = \braket{\psi | \mathcal{U}^i | \psi} = \braket{\mathcal{U}^i}_\psi.
\end{align*}
Therefore we may write,
\begin{align*}
	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}_{\psi}} = \begin{pmatrix}
 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
  \braket{\mathcal{U}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \hdots &  \braket{\mathcal{U}^{2}}_{\psi}^* \\
    \braket{\mathcal{U}^{2}}_{\psi}^* &  \braket{\mathcal{U}}_{\psi}^*  & 1 & \hdots &  \braket{\mathcal{U}^{3}}_{\psi}^* \\
   \vdots & \vdots & \vdots & \ddots & \vdots \\
  \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi}  & \braket{\mathcal{U}^{3}}_{\psi}  & \hdots &  1 
\end{pmatrix}.
\end{align*}

This confirms the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the one above it. In other words the Gram matrix of $\mathbb{Z}/n\mathbb{Z}$ matrices are circulant matrixes. This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks\cite{circulantMatrices}.

Moreover we can compute the Gram matrix of a group generated ensemble by generating the Cayley table, also known as the \emph{multiplication table}, of the group. For instance, let us consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle. If we denote the identity as $e$, the 3 symmetries as $p$, $q$ and $s$ and a rotation as $s$, we know the Cayley table to be,
\begin{table}[H]
	\centering
	\caption{Cayley table of the $S_3$ group.}
	\begin{tabular}{c||c c c c c c c}
        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
        $e$   & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
        $s^2$ & $s^2$ & $e$ & $s$ & $r$ & $p$ & $q$ \\
        $s$   & $s$ & $s^2$ & $e$ & $q$ & $r$ & $p$ \\
        $p$ & $p$ & $r$ & $q$ & $e$ & $s^2$ & $s$ \\
        $q$ & $q$ & $p$ & $r$ & $s$ & $e$ & $s^2$ \\
        $r$ & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$
    \end{tabular}
\end{table}

where we have enforced the diagonal elements to be the identity. Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product.} we immediatelly realize the Gram matrix of the $S_3$ group generated ensemble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$. In other words the Gram matrix is nothing but,
\begin{align*}
	\mathcal{G}^{S_3}_{\psi}=\begin{pmatrix}
        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
	\end{pmatrix}.
\end{align*}
Notice that, $\braket{e}_\psi=1$ since $e$ is the neutral element of the matrix product operation, i.e. $e=\mathds{1}$. Moreover in this particular example we can observe since $\mathcal{G}^{S_3}$ is hermitian we know that,
\begin{align*}\begin{cases}
	\braket{p}_{\psi}=&\braket{p}_{\psi}^*\\
	\braket{q}_{\psi}=&\braket{q}_{\psi}^*\\
\braket{r}_{\psi}=&\braket{r}_{\psi}^*\end{cases}&\quad \forall \ket{\psi}\in \mathcal{H}\\
\Updownarrow& \\
\braket{p}_{\psi},\braket{q}_{\psi},\braket{r}_{\psi}\in&\mathbb{R}\quad \forall \ket{\psi}\in \mathcal{H}.
\end{align*}
Therefore the unitary matrices corresponding to the triangle symmetries $p$, $q$ and $r$ are hermitian. It is inmediate this procedure can be applied for any group $G$, whic implies that computing the Cayley table is equivalent to computin the Gram matrix of the group generated ensemble.

Additionally, we will denote the cardinality of a finite group $G$\footnote{The cardinality of a group is the same as the number elements of the group.}, as $|G|$ which implies that for our case of interest of the prior probabilities scenario we may write $\eta_i=\frac{1}{|G|}$.

\subsection{Dual formulation of the problem}
Sometimes it is usefull to consider the dual version of each \emph{sdp} problem. The dual version of the exclusion task for the $\left\{\left(\rho_i,\frac{1}{n}\right)\right\}_{i=1}^n$ ensemble for the error probability with the Minimum Error (\gls{me}) protocol is,
\begin{align*}
	\tilde{P}_{\gls{me}}^e=\max_{\Gamma}&\tr{\Gamma}\\
	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}\\
	&\Gamma^\dagger=\Gamma,
\end{align*}
where $\tilde{P}$ stands for the dual version of the problem. Naturally, for the success probability the problem reads,
\begin{align*}
	\tilde{P}_{\gls{me}}^s=\min_{\Gamma}&\left(1-\tr{\Gamma}\right)\\
	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}\\
	&\Gamma^\dagger=\Gamma.
\end{align*}
\textcolor{blue}{Add the dual version for the zero error protocol.}

The dual version results specially usefull since given an POVM anzatz if the probabilities of the primal and dual problems coincide, i.e. $P=\tilde P$ we know we have found the optimal measurement.

\subsection{Previous results}
Enormous advances have been made in the exclusion task for group generated ensembles. The publication \emph{Quantum state exclusion for group-generated ensembles of pure states}\cite{MainPaper} yields a result of the actual exact success and/or error probabilities for both \gls{me} and \gls{ze} protocols for group generated ensembles. The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensemble $\left\{\left(\rho_i,\frac{1}{|G|}\right)\right\}_{i=1}^{|G|}$ corresponding to a finite group $G$, where $|G|$ denotes the number of the group's elements, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix. Additionally let us consider the set of eigenvalues $\{\lambda_i\}_{i=1}^{|G|}$ to be an ordered group, such that,
\begin{align*}
	i\leq j\quad\forall i,j\in\{1,...,|G|\}\Leftrightarrow \lambda_i\geq\lambda_j \forall i,j\in\{1,...,|G|\},
\end{align*}
or equivalently, the set is ordered from the lowest to highest eigenvalue. Hence, the exclusion probabilities for the minimum error (\gls{me}) protocol are,
\begin{align*}
	P_{\gls{me}}^e=&\max\left\{0,\left(\frac{\sqrt{\lambda_{|G|}}-\sum_{i<|G|}\sqrt{\lambda_i}}{|G|}\right)^2\right\}\\
	P_{\gls{me}}^s=&\min\left\{1,1-\left(\frac{\sqrt{\lambda_{|G|}}-\sum_{i<|G|}\sqrt{\lambda_i}}{|G|}\right)^2\right\}.
\end{align*}
Additionally, the results for the zero error (\gls{ze}) protocol are,
\begin{align*}
	P_{\gls{ze}}^e=&\max\left\{0,\frac{\sum_{i=1}^{|G|}\sqrt{\lambda_i}\left(\sqrt{\lambda_{|G|}}-\sum_{j<|G|}\sqrt{\lambda_j}\right)}{|G|}\right\}\\
	P_{\gls{ze}}^s=&\min\left\{1,1-\frac{\sum_{i=1}^{|G|}\sqrt{\lambda_i}\left(\sqrt{\lambda_{|G|}}-\sum_{j<|G|}\sqrt{\lambda_j}\right)}{|G|}\right\}.
\end{align*}
For us is crucial to remark one of the results' traitmarks: the probabilities are independent of the group. In other words, given two group generated ensembles $A$ and $B$ for 2 differnt groups $G_A$ and $G_b$ ($G_A\neq G_B$) with the same cardinality, i.e. $|G_A|=|G_B|$, we know that if the respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_b}$ have the same eigenvalues, then the exclusion probability for both protocols \gls{me} and \gls{ze} is the same. This matter is one of the cornersotnes of this project study.

>>>>

\subsection{Gram Matrix Formulation}\label{sectionGramMatrixFormulation}

Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n \times n$ positive semidefinite Hermitian matrix given by,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n} \\
		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n} \\
		\vdots & \vdots & \ddots & \vdots \\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
	\end{pmatrix},
\end{equation*}
that is, $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, the diagonal elements are equal to 1, and the Gram matrix becomes,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n} \\
		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n} \\
		\vdots & \vdots & \ddots & \vdots \\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
	\end{pmatrix}.
\end{equation*}

By construction, the Gram matrix is Hermitian,
\begin{align*}
	\mathcal{G}_{i,j}^* = (\braket{\psi_i|\psi_j})^* = \braket{\psi_j|\psi_i} = \mathcal{G}_{j,i}.
\end{align*}
Additionally, $\mathcal{G}$ is positive semidefinite. To see this, consider an arbitrary state $\ket{\Phi}$ and an orthonormal basis $\{\ket{i}\}_{i=1}^n$, then,
\begin{align*}
	\braket{\Phi|\mathcal{G}|\Phi} &= \braket{\Phi| \left( \sum_{i,j=1}^{n} \braket{\psi_i|\psi_j} \ket{i}\bra{j} \right) |\Phi} \\
	&= \sum_{i,j=1}^{n} \braket{\psi_i|\psi_j} \braket{\Phi|i} \braket{j|\Phi} \\
	&= \left\| \sum_{i=1}^{n} \braket{i|\Phi} \ket{\psi_i} \right\|^2 \\
	&\geq 0.
\end{align*}

The Gram matrix allows us to reformulate the exclusion problem in a more abstract, basis-independent manner. Since $\mathcal{G}$ is Hermitian and positive semidefinite, it can be factorized as,
\begin{align*}
	\mathcal{G} = X^\dagger X,
\end{align*}
for some matrix $X$, whose columns are the pure states,
\begin{align*}
	X = \begin{pmatrix}
		\mid & \mid &        & \mid \\
		\ket{\psi_1} & \ket{\psi_2} & \dots & \ket{\psi_n} \\
		\mid & \mid &        & \mid
	\end{pmatrix}.
\end{align*}

Let us fix an arbitrary orthonormal basis $\{\ket{\omega_i}\}_{i=1}^n$. Then, the diagonal entries of $X$ in this basis are given by,
\begin{align*}
	X_{i,i} = \braket{\omega_i|\psi_i}.
\end{align*}
\footnote{Note that fixing the basis $\{\ket{\omega_i}\}_{i=1}^n$ uniquely determines the decomposition $\mathcal{G} = X^\dagger X$, and vice versa.}We define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$. Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constraints become,
\begin{align*}
	\tr(\Pi_i \rho_i) &= \tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
	&= |\braket{\omega_i|\psi_i}|^2 \\
	&= |X_{i,i}|^2.
\end{align*}

Thus, we can reformulate the \gls{sdp} for the minimum-error (\gls{me}) protocol as,
\begin{align*}
	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i}, \\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

Similarly, the success probability becomes,
\begin{align*}
	P_{\gls{me}}^s = \max_{X} &\left( 1 - \sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i} \right), \\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

This reformulation reveals that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems under both the \gls{me} and \gls{ze} protocols are equivalent. That is, their optimal success and error probabilities coincide. Consequently, we focus on the Gram matrix to study exclusion problems rather than the explicit state representations.

Furthermore, we note that the case of arbitrary prior probabilities $\eta_i$ can be reduced to the equal prior case $\eta_i = \frac{1}{n}$ by defining non-normalized states,
\begin{align*}
	\ket{\tilde{\psi}_i} = \frac{1}{\sqrt{\eta_i}} \ket{\psi_i},
\end{align*}
and reformulating the problem in terms of these states. The prior probabilities are then absorbed into the state norm. Therefore, without loss of generality, in this project we will assume equal prior probabilities.

@@

Given a quantum state $\ket{\psi}$, referred to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$. Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form
\begin{align*}
	U_i\ket{\psi}, \quad i \in \{1, \dots, n\},
\end{align*}
where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix multiplication. In terms of density matrices, the ensemble can equivalently be written as,
\begin{align*}
	\rho_i = U_i \rho U_i^\dagger, \quad i \in \{1, \dots, n\},
\end{align*}
where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix corresponding to the seed state.

For instance, let $\mathcal{U}$ be a unitary operator such that $\mathcal{U}^n = \mathds{1}$ (i.e., $\mathcal{U}$ generates a cyclic group of order $n$). Then, the set of states
\begin{align*}
	\left\{ \mathcal{U}^i\ket{\psi} \right\}_{i=0}^{n-1},
\end{align*}
forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$. This type of ensemble is of particular interest in our study and will be explored in more detail in a subsequent section.

\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state. The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are
\begin{align*}
	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \braket{\psi | \mathcal{U}^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
\end{align*}
where we use the shorthand notation,
\begin{align*}
	\braket{\mathcal{U}^k}_\psi := \braket{\psi | \mathcal{U}^k | \psi}.
\end{align*}

@@

Note that the Gram matrix is Hermitian, as expected, since
\begin{align*}
    \braket{\mathcal{U}^{-j}}_{\psi} = \braket{\psi | \mathcal{U}^{-j} | \psi} = \left(\braket{\psi | \mathcal{U}^j | \psi}\right)^* = \braket{\mathcal{U}^j}_{\psi}^*.
\end{align*}
Additionally, by using the identity $\mathcal{U}^n = \mathds{1}$, we can simplify expressions such as,
\begin{align*}
	\braket{\mathcal{U}^{-n+i}}_\psi = \braket{\psi | \mathcal{U}^{-n+i} | \psi} = \braket{\psi | \mathcal{U}^i | \psi} = \braket{\mathcal{U}^i}_\psi.
\end{align*}
Thus, we may write,
\begin{align*}
	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{\psi} = \begin{pmatrix}
 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
 \braket{\mathcal{U}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \hdots &  \braket{\mathcal{U}^{2}}_{\psi}^* \\
 \braket{\mathcal{U}^{2}}_{\psi}^* & \braket{\mathcal{U}}_{\psi}^* & 1 & \hdots &  \braket{\mathcal{U}^{3}}_{\psi}^* \\
 \vdots & \vdots & \vdots & \ddots & \vdots \\
 \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \braket{\mathcal{U}^{3}}_{\psi} & \hdots & 1 
\end{pmatrix}.
\end{align*}

This shows the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the previous one. In other words, the Gram matrices of $\mathbb{Z}/n\mathbb{Z}$-generated ensembles are circulant matrices. This structure is particularly useful, as circulant matrices can be diagonalized by the discrete Fourier basis, greatly simplifying many computations~\cite{circulantMatrices}.

The Fourier basis for an $n \times n$ circulant matrix consists of the set of vectors $\{\omega_i\}_{i=1}^n$, where
\begin{align*}
	\omega_i = \frac{1}{\sqrt{n}} (1, \gamma^i, \gamma^{2i}, \ldots, \gamma^{i(n-1)})^T,
\end{align*}
and
\begin{align*}
	\gamma = e^{\frac{2\pi i}{n}}.
\end{align*}

Moreover, we can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group. For example, consider the smallest non-commutative group, $S_3$, consisting of the symmetries and rotations of an equilateral triangle. Denoting the identity as $e$, the rotations elements as $s$, $s^2$ (one being the result of 2 times the other) and the symmetries $p$, $q$, and $r$, the Cayley table is,

\begin{table}[H]
	\centering
	\caption{Cayley table of the $S_3$ group.}
	\begin{tabular}{c||c c c c c c}
        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
        $e$   & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
        $s^2$ & $s^2$ & $e$ & $s$ & $r$ & $p$ & $q$ \\
        $s$   & $s$ & $s^2$ & $e$ & $q$ & $r$ & $p$ \\
        $p$   & $p$ & $r$ & $q$ & $e$ & $s^2$ & $s$ \\
        $q$   & $q$ & $p$ & $r$ & $s$ & $e$ & $s^2$ \\
        $r$   & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$
    \end{tabular}
\end{table}

We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}. It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$. That is,
\begin{align*}
	\mathcal{G}^{S_3}_{\psi} = \begin{pmatrix}
        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
	\end{pmatrix}.
\end{align*}
Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude:
\begin{align*}
\braket{p}_{\psi},\ \braket{q}_{\psi},\ \braket{r}_{\psi} \in \mathbb{R}, \quad \forall \ket{\psi} \in \mathcal{H},
\end{align*}
which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian. As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.

Finally, we denote the cardinality of a finite group $G$ (i.e., the number of its elements) as $|G|$. In scenarios with uniform prior probabilities, this implies,
\begin{align*}
	\eta_i = \frac{1}{|G|}\quad \forall i\in\{1,...,n\}.
\end{align*}
\subsection{Dual Formulation of the Problem}

It is often useful to consider the \emph{dual} version of a \gls{sdp} problem, as it provides both conceptual insights and practical advantages for verifying optimality.

Consider the ensemble $\left\{ \left( \rho_i, \frac{1}{n} \right) \right\}_{i=1}^n$, where each state $\rho_i$ appears with uniform prior probability $1/n$. The dual SDP corresponding to the Minimum Error (\gls{me}) exclusion protocol, when expressed in terms of the error probability, is given by,
\begin{align*}
	\tilde{P}_{\gls{me}}^e = \max_{\Gamma} \quad & \tr{\Gamma} \\
	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
	& \Gamma^\dagger = \Gamma,
\end{align*}
where $\tilde{P}$ denotes the dual version of the problem.

Similarly, the dual SDP for the success probability in the same protocol reads:
\begin{align*}
	\tilde{P}_{\gls{me}}^s = \min_{\Gamma} \quad & 1 - \tr{\Gamma} \\
	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
	& \Gamma^\dagger = \Gamma.
\end{align*}

\textcolor{blue}{Add the dual version for the zero error protocol.}

In the case of the zero-error exclusion protocol, the dual SDP formulation becomes

One of the primary uses of the dual formulation is in establishing optimality. If a POVM ansatz yields equal objective values for both the primal and dual problems, i.e., $P = \tilde{P}$, then strong duality holds and the measurement is guaranteed to be optimal.

This duality principle not only provides a tool for verification but also suggests constructive approaches to discovering optimal measurements, especially in structured ensembles such as those generated by group actions.
\subsection{Previous Results}\label{sectionPreviousResults}

Significant progress has been made in the study of the state exclusion task for group-generated ensembles. In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error \gls{me} and Zero Error \gls{ze} exclusion protocols.

Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$. Assume the eigenvalues are ordered increasingly,
\begin{align*}
	i \leq j \quad \Leftrightarrow \quad \lambda_i \leq \lambda_j, \quad \forall i,j \in \{1, \dots, |G|\},
\end{align*}
i.e., $\lambda_1$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.

The exclusion probabilities under the Minimum Error protocol are given by,
\begin{align*}
	P_{\gls{me}}^e &= \max\left\{ 0, \left( \frac{ \sqrt{\lambda_{|G|}} - \sum_{i<|G|} \sqrt{\lambda_i} }{|G|} \right)^2 \right\}, \\
	P_{\gls{me}}^s &= \min\left\{ 1, 1 - \left( \frac{ \sqrt{\lambda_{|G|}} - \sum_{i<|G|} \sqrt{\lambda_i} }{|G|} \right)^2 \right\}.
\end{align*}

For the Zero Error protocol, the corresponding expressions arem
\begin{align*}
	P_{\gls{ze}}^e &= \max\left\{ 0, \frac{ \sum_{i=1}^{|G|} \sqrt{\lambda_i} \left( \sqrt{\lambda_{|G|}} - \sum_{j<|G|} \sqrt{\lambda_j} \right) }{|G|} \right\}, \\
	P_{\gls{ze}}^s &= \min\left\{ 1, 1 - \frac{ \sum_{i=1}^{|G|} \sqrt{\lambda_i} \left( \sqrt{\lambda_{|G|}} - \sum_{j<|G|} \sqrt{\lambda_j} \right) }{|G|} \right\}.
\end{align*}
